A general and efficient representation of Ancestral Recombination Graphs

### 2023-10-06 paper.tex
Tweaks

[TODO finish up with a positive note about interchange, and make the point
clearly that tskit is an ARG library. Splice in the stuff about haplotype
blocks and ARGON format here somewhere --- basically this is a derived product
of the gARG encoding, so while there are some computation advantages it's not
fundamendal to the actual representation of the thing]
In summary, we advocate for decoupling between generative models that give rise to observed data and data formats that can faithfully and realistically encode these data. We have shown that ``genome'' ARG (gARG) encoding enables flexible encoding of today's datasets with realistic levels of precision. Importantly, genome ARG encoding should facilitate easier data interchange between different tools, which will in turn support active research in this area.

>>>>

[TODO finish up with a positive note about interchange, and make the point
clearly that tskit is an ARG library. Splice in the stuff about haplotype
blocks and ARGON format here somewhere --- basically this is a derived product
of the gARG encoding, so while there are some computation advantages it's not
fundamental to the actual representation of the thing]
In summary, we advocate for decoupling between generative models that give rise to observed data and data formats that can faithfully and realistically encode these data. We have shown that ``genome'' ARG (gARG) encoding enables flexible encoding of today's datasets with realistic levels of precision. Importantly, genome ARG encoding should facilitate easier data interchange between different tools, which will in turn support active research in this area.
